True Lies

### 2018-11-08 GSV-comment-brief.Rmd
Add the word Abstract to the abstract, because apparently it wasn't obvious enough for Springer.

> Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability
> distribution of the proportion of lies told in "coin flip" style experiments. I show that their
> estimates and confidence intervals are flawed. I demonstrate two better ways to estimate the 
> probability distribution of what we are really interested in: the proportion of liars.

>>>>

> **Abstract**: Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability
> distribution of the proportion of lies told in "coin flip" style experiments. I show that their
> estimates and confidence intervals are flawed. I demonstrate two better ways to estimate the 
> probability distribution of what we are really interested in: the proportion of liars.
